Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM

### 2010-10-28 results.tex
Results section improved

\newpage

@@

First of all, the low-order FEM and $hp$-FEM were compared.
Comparison of single mesh H\_ANISO with p=1, single mesh H\_ANISO with p=2
and single mesh HP\_ANISO should be added here to make the point that 
hp-FEM is much better than low-order FEM. 
Otherwise the reader does not know 
why we are just using hp-FEM in the following. Or is there a reason 
why you do not want to add this here --  long computing time for hp-FEM or something 
else?

@@

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{singlemulti_dof}
  \caption{\label{fig:singlemultidof} Number of degrees of freedom (DOF) as a function 
  of physical time for single-mesh and multi-mesh configurations with the HP\_ISO
  and HP\_ANISO adaptivity modes. Note logarithmic scale on the vertical axis.}
\vspace{-6mm}
  \end{centering}
\end{figure}

@@

These result are in good agreement with Fig.~\ref{fig:cphi-2} -- in the vicinity
of the boundaries $\partial \Omega_1$ and $\partial\Omega_3$, the concentration gradient
is much greater than the voltage gradient. Therefore the multimesh $hp$-FEM adaptivity 
algorithm has increased the maximum polynomial degree for the $C$-space to~7 while 
the maximum polynomial degree for the $\phi$-space is~2. One can also see that the mesh 
is significantly more refined for $C$.
Since these results are representative for all adaptivity modes, only multi-mesh 
configurations are considered in the following.

@@

\subsection{Optimization of the HP\_ANISO and HP\_ANISO\_P adaptivity modes}

>>>>

%\newpage

@@

First of all, the low-order FEM and $hp$-FEM were compared. A single mesh
H\_ANISO with polynomial degrees $p=1$ and $p=2$ were compared to
HP\_ANISO mode. The coarse initial mesh as shown in Fig.~\ref{fig:mesh}~(a)
was used in the solutions.
The results are shown in Figs.~\ref{fig:singlehhpdof} 
and~\ref{fig:singlehhpcpu}.
\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{singleh_hp_dof}
  \caption{\label{fig:singlehhpdof} Number of degrees of freedom (DOF) as a function 
  of physical time for single-mesh H\_ANISO (in case of
  $p=1$ and $p=2$) and single-mesh HP\_ANISO.}
  \end{centering}
\end{figure}

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{singleh_hp_cpu}
  \caption{\label{fig:singlehhpcpu} Cumulative CPU time as a function 
  of physical time for single-mesh H\_ANISO (in case of $p=1$ and $p=2$)
  and single mesh HP\_ANISO.}
  \end{centering}
\end{figure}

\noindent
It can be seen that $hp$-FEM results in the shorter computing 
time and smaller number
of degrees of freedom (DOF) than the low-order FEM. The same holds true
for H\_ISO and HP\_ISO modes. In fact, in case of H\_ISO the relative error did not
converge to the pre-set threshold value of $0.5\%$.
Therefore, the $h$-FEM solutions will be omitted from the further comparisons.
Instead, only $hp$-FEM solutions on the coarse mesh and $p$-FEM solutions
on the fine mesh will be discussed. It must be also noted that the error
converged to or below $0.5\%$ for all $p$-FEM and $hp$-FEM results, therefore
the error graphs will not be presented.

@@

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{singlemulti_dof}
  \caption{\label{fig:singlemultidof} Number of degrees of freedom (DOF) as a function 
  of physical time for single-mesh and multi-mesh configurations with the HP\_ISO
  and HP\_ANISO adaptivity modes. Note logarithmic scale on the vertical axis.}
%\vspace{-6mm}
  \end{centering}
\end{figure}

@@

These result are in good agreement with Fig.~\ref{fig:cphi-2} --- in the vicinity
of the boundaries $\partial \Omega_1$ and $\partial\Omega_3$, the concentration gradient
is much greater than the voltage gradient. Therefore the multimesh $hp$-FEM adaptivity 
algorithm has increased the maximum polynomial degree for the $C$-space to~7 while 
the maximum polynomial degree for the $\phi$-space is~2. One can also see that the mesh 
is significantly more refined for $C$.
Since these results are representative for all adaptivity modes, only multi-mesh 
configurations are considered in the following.

@@

\subsection{Optimization of the HP\_ANISO adaptivity modes}
